Environmental behaviour & practices

### 2021-01-15 01-Sustainable-indicators.Rmd
sorting the site from teams de drive
improving 1%

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 01-Sustainable-indicators.bib
nocite: '@*'
editor_options: 
  chunk_output_type: console
---

@@

#library(rticles)
#library(rmarkdown)
#render("01-Sustainable-indicators.Rmd", output_format = "word_document")
#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document")
#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article")

@@

@@

The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@ref]. 
The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to propose additoanl cascading loops  to certain types plastic waste. 
More precisely, the use of recycled assets in the printing process chaing of additive manufacturing technology can give add value to wastes to create possible products or scientific equipement a a lower cost than the commercial.
In a sense, this apporache could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe.

>>>>

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 01-Sustainable-indicators.bib
bibliography: library.bib
nocite: '@*'
editor_options: 
  chunk_output_type: console
---

@@

#library(rticles)
#library(rmarkdown)
#render("01-Sustainable-indicators.Rmd", output_format = "word_document", output_dir = "01-Sustainable-Indicators")
#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document", output_dir = "01-Sustainable-Indicators")
#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article", output_dir = "01-Sustainable-Indicators")

@@

## Mind mapping

```{r, include=FALSE}
library('mindr')
### text -> widget
input <- c("# Chapter 1", "## Section 1.1", "## Section 1.2", "# Chapter 2")
mm(from = input, type = "text", root = "Ideas to develop")

input <- system.file("examples/md/bookdownplus1.md", package = "mindr")
mm(from = input, type = "file", root = "mindr")

:::l-page
<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
:::

@@

The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@reference]. 
The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to propose additoanl cascading loops  to certain types plastic waste. 
More precisely, the use of recycled assets in the printing process chaing of additive manufacturing technology can give add value to wastes to create possible products or scientific equipement a a lower cost than the commercial.
In a sense, this apporache could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe.

### 2021-01-15 02-supply-chain.Rmd
improving 1%

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 02-supply-chain.bib
#nocite: '@*'

>>>>

---
title: "Supply chain Axis"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 02-supply-chain.bib
#nocite: '@*'

### 2021-01-15 03-comportements.Rmd
adding PPS&Q article Sustainable Indicators
improving 1%

---
title: "Sustainable behaviour"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 03-comportement.bib
nocite: '@*'

@@

>>>>

---
title: "Environmental behaviour & practices"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 03-comportement.bib
nocite: '@*'

@@

- Chan, L., Bishop, B., 2013. A moral basis for recycling: Extending the theory of planned behaviour. J. Environ. Psychol. 36, 96–102. https://doi.org/10.1016/j.jenvp.2013.07.010
